Local simple connectedness of boundaries of hyperbolic groups

### 2020-10-01 paper.tex
Improved some phrasing

It is natural to ask whether a similar result holds in which the assumption on
the topology of point complements in $\boundary G$ is replaced by a similar
assumption on the whole of the boundary. This question is discussed in
Section~\ref{sec:conclusion}. Note however that one direction of this question
can be proved as a corollary of Theorem~\ref{thm:main_theorem}, at least when
circular boundaries (for which the implication does not hold) are excepted.

>>>>

It is natural to ask whether a similar result holds in which the condition on
the topology of point complements in $\boundary G$ is replaced by a similar
condition on the whole of the boundary. This question is discussed in
Section~\ref{sec:conclusion}. One direction of this question can be answered as
a corollary of Theorem~\ref{thm:main_theorem}, as long as circular boundaries
(for which the implication does not hold) are excepted.
